Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-31 paper/paper.tex
paper: Add Results Discussion

Tras la presentación objetiva de los resultados, querrás aportar una discusión de los mismos.

>>>>

We have applied our proposed method to clusters with different typologies:

\begin{itemize}
  \item NGC 2516 (Ap. \ref{sec:ngc2516}) has it proper motion center deviated from the origin but
        it is embedded inside a big cloud of stars with similar proper motions.
  \item NGC 2632 (Ap. \ref{sec:ngc2632}), in addition to Melotte 22, ia s cluster whose proper motion center
        is not located at the origin and has a well separated parallax center.
  \item NGC 2682 (Ap. \ref{sec:ngc2682}), on the other hand, has its parallax centered within the region's gaussian,
        which complicates its detection although its proper motion center is deviated from the origin.
  \item Melotte 22 (Ap. \ref{sec:melotte22}), as well as Melotte 25, is a cluster closer to us than the other.
        That makes its membership stars to be more scattered than previous clusters which are more compact.
\end{itemize}

All these clusters have a wide variety of diameters, from 25 to 330 arcmin,
as well as the number of stars that belong to them. NGC 2682 has 3,000 stars while
Melotte 25 is composed by more than 400,000 stars. More information about the
studied clusters is available in Table \ref{tab:clusters_summary}.

\begin{table}[htbp]
  \begin{center}
    \resizebox{\columnwidth}{!}{
      \begin{tabular}{l|c|c|c|c}
        \textbf{OC} & \emph{$\alpha$ J2000 $(degrees)$} & \emph{$\delta$ J2000 $(degrees)$} & \emph{Radius $(arcmin)$} & \emph{\# stars} \\
        \hline
        NGC 2516 & 119.517 & -60.753 & 15 & 12,869 \\
        NGC 2632 & 130.1 & 19.667 & 35 & 13,167 \\
        NGC 2682 & 132.825 & 11.8 & 12.5 & 2,839 \\
        Melotte 22 & 56.75 & 24.117 & 60 & 61,552 \\
        Melotte 25 & 66.725 & 15.867 & 165 & 433,996 \\
      \end{tabular}
    }
    \caption{Righ ascension, declination, radius and number of stars of studied clusters.
             The number of stars corresponds to those stars contained within a cone of center
             $(\alpha, \delta)$ and raius the cluster's radius multiplied by a factor of 1.5.}
    \label{tab:clusters_summary}
  \end{center}
\end{table}

In all cases, the model has resolved properly the identity of the cluster
and has characterized the membership stars, giving compatible results
with the ones obtained with classic procedures and VO tools.

Compared with the mentioned tools, our model can be categorized as a
non-parameterized model since it does not depend on parameters referred
to the cluster itself but only hyperparameters such as the initial number
of clusters to be found, or the structure of the Clustering Layer used by DEC model.

The proposed method is also non-supervised since we do not need to tell the model
which stars belong to the cluster or assist it while its training stage.

Only at the end of the characterization, a fine tuning driven by the user,
can be applied in order to improve the selection by discarding those
stars which fall outside the given quantiles.

In any case, we do not make assumptions about the cluster profile,
something that we have to take into account when using VO tools.
This is another evidence that our model is non-parameterized.
